Low Complexity Adaptive Sonar Imaging

### 2016-03-02 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2016:03:02	12:55:42	(on. 2.mars)

A much faster and simpler alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. Based on an idea by Vignon~\cite{Vignon2008}, it was first introduced by Synnev\aa{}g \emph{et al}. in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar image quality to MVDR in systems with focused transmit beams. LCA applies a set of predefined windows, or apodization weights, and selects the one offering the best sidelobe suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a reduced window solution space. Alternatively, it may be viewed as a multi-apodization technique. One such method is described by Stankwitz \emph{et al}. in radar imaging~\cite{Stankwitz1995}, where the best out of 2 or 3 windows are selected. However, LCA is different in that it typically selects from a larger pool of windows and allows micro-steered variations of them. This gives LCA an adaptive freedom that is somewhere in between that of traditional multi-apodization techniques and MVDR.

@@

To test the performance of the MVDR and LCA beamformers, we have processed data acquired by the Kongsberg Maritime HUGIN AUV carrying their 32 element HISAS1030 sonar~\cite{Hansen2011}. It is a high resolution synthetic aperture sonar with 1.2\;m array length, 100\;kHz operating frequency, 30\;kHz bandwidth and 23$^\circ$ receiver element -3\,dB opening angle.

>>>>

A much faster and simpler alternative to MVDR is the Low Complexity Adaptive (LCA) beamformer. Based on an idea by Vignon~\cite{Vignon2008}, it was first introduced by Synnev\aa{}g \emph{et al}. in clinical medical imaging~\cite{Synnevag2008}, who demonstrated its ability to obtain very similar image quality to MVDR in systems with focused transmit beams. LCA applies a set of predefined windows, or apodization weights, and selects the one offering the best sidelobe suppression. It relies on the same optimization criterion as MVDR, thus may be considered a version of MVDR with a discrete and static window solution space. Alternatively, it may be viewed as a multi-apodization technique. One such method is described by Stankwitz \emph{et al}. in radar imaging~\cite{Stankwitz1995}, where the best out of 2 or 3 windows are selected. However, LCA is different in that it typically selects from a larger pool of windows and allows micro-steered variations of them. This gives LCA an adaptive freedom that is somewhere in between that of traditional multi-apodization techniques and MVDR. The bigger the space the weights span, the greater the adaptive freedom, but only the solutions that are valid in the constrained solution space can make a difference.

@@

To test the performance of the MVDR and LCA beamformers, we have processed data acquired by the Kongsberg Maritime HUGIN AUV carrying their 32 element HISAS1030 sonar~\cite{Hansen2011}. It is a high resolution synthetic aperture sonar with 1.2\;m array length, 100\;kHz operating frequency, 30\;kHz bandwidth and 23$^\circ$ element -3\,dB opening angle.

### 2016-03-02 LCAforActiveSonarImaging/submission/submit1/answer/answer.tex
la2pdf commit - 2016:03:02	12:55:42	(on. 2.mars)

\begin{enumerate}
% \emph{General}
\hi{Abstract}
\qi{"the array's spatial covariance matrix" might be a bit shocking for the non-expert Reader $\rightarrow$ The formulation in the Introduction might fit better "the influence of noise ..."}
\ai{This is a good point. We have reformulated the sentence to speak of computing the spatial statistics instead.}
%
\hi{Page 2}
\qi{"6 of which were micro-steered" --> a short explanation or reference might help to understand what is meant by "micro-steered"}
\ai{Another good point. This wording is now changed and a sentence elaborating on its meaning is added.}
%
\qi{"it was not clear how how many" --> delete 1 x "how"}
\ai{Thank you. Corrected.}
%
\qi{"with an element beamwidth" --> what is meant by element beamwidth? Maybe an additional figure could be used to explain this.}
\ai{Good remark. We meant the -3dB opening angle of the elements. Changes are now made to reflect this.}
%
\hi{Page 3, after (1)}
\qi{"Applying a window that trails off .... Minimum variance distortion-less response (MVDR) beamformer."--> real and complex Windows? The introduction should be more formal: x ist introduced as delayed data, weights or delays to change, or both is explained later. --> The difference between noise and sidelobes should be pointed out.}
\ai{}
%
\hi{Page 5, equation (5)}
\qi{The lateral correlation and the reason why equation (5) is a good choice should be better explained.}
\ai{Indeed it should, this paragraph is now rewritten.}
%
\hi{Page 6, last row}
\qi{"they are optimal for any value" --> optimal in which sense?}
\ai{Thank you. This was mentioned earlier in the same paragraph, just after (8).}
%
\hi{Fig 3}
\qi{why is a 40x40 pixel group a good choice? could the associated broadside direction be made visible in the figure, too?}
\ai{This is an excellent question. This should perhaps be related to the detail level in the image, which in turn depends on the array's imaging performance.}
%
\hi{Page 8}
\qi{reference to Fig.1 --> could the sequence of figures be changes to have Fig. 1 closer to this paragraph}
\ai{Valid point. In our two column print the figure is on the page before its first reference. }
%
\hi{Page 11}
\qi{where is the synthetic aperture needed/applied in this work, or is it just the name of the array? how does the work on LCA/MVDR Change the Quality of synthetic aperture?
what exactly is the sectorscan mode?}
\ai{Thank you, we see that our formulation should be clarified. We are creating an image of the sector highlighted by a single ping of data (sectorscan), but are using data recorded by a synthetic aperture sonar (SAS). We mention it since SAS systems have a wide transmit beam intended to highlight multiple pings and thus does not produce the best sectorscan images.}
%
\end{enumerate}

>>>>

\begin{enumerate}
% \emph{General}
\hi{Abstract}
\qi{"the array's spatial covariance matrix" might be a bit shocking for the non-expert Reader $\rightarrow$ The formulation in the Introduction might fit better "the influence of noise ..."}
\ai{This is a good point. We have reformulated the sentence to speak of computing the spatial statistics instead.}
%
\hi{Page 2}
\qi{"6 of which were micro-steered" $\rightarrow$ a short explanation or reference might help to understand what is meant by "micro-steered"}
\ai{Another good point. This wording is now changed and a sentence elaborating on its meaning is added.}
%
\qi{"it was not clear how how many" $\rightarrow$ delete 1 x "how"}
\ai{Thank you. Corrected.}
%
\qi{"with an element beamwidth" $\rightarrow$ what is meant by element beamwidth? Maybe an additional figure could be used to explain this.}
\ai{Good remark. We meant the -3dB opening angle of the elements. We have reworded this the two places it is mentioned.}
%
\hi{Page 3, after (1)}
\qi{"Applying a window that trails off .... Minimum variance distortion-less response (MVDR) beamformer." $\rightarrow$ real and complex Windows? The introduction should be more formal: x ist introduced as delayed data, weights or delays to change, or both is explained later. $\rightarrow$ The difference between noise and sidelobes should be pointed out.}
\ai{}
%
\hi{Page 5, equation (5)}
\qi{The lateral correlation and the reason why equation (5) is a good choice should be better explained.}
\ai{Indeed it should, this paragraph is now rewritten.}
%
\hi{Page 6, last row}
\qi{"they are optimal for any value" $\rightarrow$ optimal in which sense?}
\ai{Thank you. This was mentioned earlier in the same paragraph, just after (8).}
%
\hi{Fig 3}
\qi{why is a 40x40 pixel group a good choice? could the associated broadside direction be made visible in the figure, too?}
\ai{This is an excellent question. This should perhaps be related to the detail level in the image, which in turn depends on the array's imaging performance.}
%
\hi{Page 8}
\qi{reference to Fig.1 $\rightarrow$ could the sequence of figures be changes to have Fig. 1 closer to this paragraph}
\ai{Valid point. In our two column print the figure is on the page before its first reference. }
%
\hi{Page 11}
\qi{where is the synthetic aperture needed/applied in this work, or is it just the name of the array? how does the work on LCA/MVDR Change the Quality of synthetic aperture?
what exactly is the sectorscan mode?}
\ai{Thank you, we see that our formulation should be clarified. We are creating an image of the sector highlighted by a single ping of data (sectorscan), but are using data recorded by a synthetic aperture sonar (SAS). We mention it since SAS systems have a wide transmit beam intended to highlight multiple pings and thus does not produce the best sectorscan images.}
%
\end{enumerate}
